\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-04-07 docs/paper/paper.tex
* ANN * Started working on experiments

Generative adversarial networks are introduced in \cite{goodfellow2014generative}. We have employed GAN to augment the number of samples that are used in training. A GAN is composed of two neural networks: generator and discriminator. The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset. Discriminator assesses the performance of the generator and provides feedback for training. Instead of directly training generator, it is trained through this feedback. This paradigm avoids over-fitting the data in the generator side.

@@

		\draw [training] (latent) -- (generator) node [pos=.5, right, xshift=0.1cm] (z) {Latent variable};
		\draw [training] (generator) -- (generated);
		\draw [training] (generated) -| (critic);
		\draw [training] (collected) -| (critic);
		\draw [training] (critic) -- (metric);
		\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
		\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
	\end{tikzpicture}
	\caption{WGAN training}
	\label{fig:gan}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
		Hidden layers & 5 & 5 \\
		Neurons & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ \\
		Activation & ReLU & Leaky ReLU \\
		Optimizer & Adam [ref] & Adam [ref] \\
		Normalization & - & Batch \cite{ioffe2015batch} \\
	\end{tabular}
	\caption{Details of WGAN model}
	\label{tbl:gandetails}
\end{table}

@@

Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function. To reduce overfitting we use the Early stopping method, that is by saving checkpoints where the best validation mean squared error occurred as we iterate. To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used \cite{ioffe2015batch}.

We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected. Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
Previous works \cite{ravuri2019seeing, shmelkov2018good}, demonstrated that random data augmentation actually had weakened the performance of the model. Hence, active researches are ongoing to find ways to optimally sample the generated data \cite{bhattarai2019sampling}, in other words to filter out the "good" generated data after training the GAN. In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables, and the confinement loss. In the following sub-sections we discuss the networks architectures. Before we proceed, it is worth mentioning that the choices made for the parameters of the networks are by no means a robust set of rules, rather, they are rules of thumb and heuristics, as no such rules have been yet developed for ANN models.

\subsection{Artificial neural network design}
\label{ssec:ann}
The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers. Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.  Table \ref{tbl:anndetails} summarizes the details of the model. Due to the nature of the problem, over-fitting is an important issue. We have used early stopping method [ref] to reduce over-fitting. \hl{This method works by saving checkpoints where the best validation mean squared error occurred as it iterates before the model starts to over-fit.} To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm \cite{ioffe2015batch} was used.

\begin{table}[h]
\centering
    \begin{tabular}{|l|l|}
    \hline
Number of hidden layers & 6  \\
\hline
Number of neurons per hidden layers & 50  \\
\hline
Activation function & Rectified Linear Unit (ReLU)  \\
\hline
Optimizer & Adam\cite{kingma2014adam}  \\
\hline
Loss function& Mean Squared Error (MSE) \\
\hline
    \end{tabular}
\caption{Detailes of the ANN model}
\label{tbl:anndetails}
\end{table}

@@

@@

A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM. This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent. This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)). Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing. By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection. In contrast, randomly shuffling the data set as a whole is an easy task in this situation, and the ANN model would make great predictions on the test set, however a sense of generality towards new geometric sets will be lost.

>>>>

Generative adversarial networks are introduced in \cite{goodfellow2014generative}. We have employed GAN to augment the number of samples that are used in training. A GAN is composed of two neural networks: generator and discriminator. The aim of the generator is to transform fully randomized data into data that follows the distribution of the original dataset. Discriminator assesses the performance of the generator and provides feedback for training. Instead of directly training generator, it is trained through this feedback. This paradigm avoids over-fitting the data.

@@

		\draw [training] (latent) -- (generator) node [pos=.5, left, xshift=-0.1cm] (z) {Latent variable};
		\draw [training] (generator) -- (generated);
		\draw [training] (generated) -| (critic);
		\draw [training] (collected) -| (critic);
		\draw [training] (critic) -- (metric);
		\draw [testing]  (metric.east) - ++(1,0) |-  (critic.east);
		\draw [testing]  (metric.west) - ++(-2.2,0) |-  (generator.west);
	\end{tikzpicture}
	\caption{WGAN training}
	\label{fig:gan}
\end{figure}

\begin{table}
	\centering
	\begin{tabular}{l|l|l}
		\textbf{Parameter} & \textbf{Generator} & \textbf{Critic} \\\hline
		Hidden layers & 5 & 5 \\
		Neurons & $ 2^{2}~batchsize $ & $2^{layers}~batchsize$ \\
		Activation & ReLU & Leaky ReLU \\
		Optimizer & Adam \cite{kingma2014adam} & Adam \cite{kingma2014adam} \\
		Normalization & - & Batch \cite{ioffe2015batch} \\
	\end{tabular}
	\caption{Details of WGAN model}
	\label{tbl:gandetails}
\end{table}

@@

The ANN model employed in this research is a fully-connected feed-forward Multi Layer Perceptron (MLP) consists of an input layer, an output layer, and 5 hidden layers. Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function.  Table \ref{tbl:anndetails} summarizes the details of this model. We have adopted Adam \cite{kingma2014adam} as the optimizer and the mean squared error as the loss/cost function.

Due to the nature of the problem, over-fitting is an important issue. We have used early stopping method to reduce over-fitting. In this method, it is possible to terminate and go back to a previous state if overall validation error increases. Thus instead of being forced into a worse classifier, training is terminated earlier. In addition, we use Batch Normalization algorithm \cite{ioffe2015batch} to accelerate training, reduce the effects of initial randomized state and mitigate the problem of internal covariate shift.

In proposed system, the ANN is trained using the samples from the original dataset and the augmented samples generated by the GAN phase. Please note that the samples that are selected to be used in training is not used in the training phase.

\begin{table}
\centering
    \begin{tabular}{l|l}
		Hidden layers & 6  \\
		\hline
		Neurons per hidden layer & 50  \\
		\hline
		Activation function & Rectified Linear Unit (ReLU)  \\
		\hline
		Optimizer & Adam\cite{kingma2014adam}  \\
		\hline
		Loss function& Mean Squared Error (MSE) \\
    \end{tabular}
	\caption{Detailes of the ANN model}
	\label{tbl:anndetails}
\end{table}

@@

A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM. This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36)).

@@

In order to prove the effectiveness of the proposed setup, we have performed multiple experiments over two datasets. We have built the first dataset that is used in the experiments. This is \hl{an SPR PCF configuration ... and collected using FV-FEM.} Details of this dataset is explained in Section \ref{sec:pcf}. Seven configurations were randomly selected for training both the GAN and the ANN, one configuration was held out for validation, and the last one is used for testing. Slicing the data this way allowed us to guide the network to predict the loss on a completely different configuration.

Additionally, we have used the dataset that has been used in [paper0]. \hl{This dataset contains 1000 samples. Inputs to this data is .... and outputs are ....} We have only used confinement loss for the output.

By slicing the data set this way we are guiding the network to learn an entirely new set of geometric properties, and this is the reason what made the task impossible, since we only have nine configurations, as we discussed at the beginning of this subsection. In contrast, randomly shuffling the data set as a whole is an easy task in this situation, and the ANN model would make great predictions on the test set, however a sense of generality towards new geometric sets will be lost.
